%%
%%  Department of Electrical, Electronic and Computer Engineering.
%%  EPR400/2 Final Report - Preamble.
%%  Copyright (C) 2011-2018 University of Pretoria.
%%

This document is a report showing the work that I did in designing a home shopping list device. The device was designed using data structures and algorithms as well as digitally communicating components.
\\[2ex]
\textit{Project proposal and technical documentation} \newline
A copy of the approved Project Proposal is contained in Part 3 of this report and technical documentation is also included in Part 5 of the report. The technical section of the report documents the hardware schematics and the software code implemented. This appendix is included on a CD that accompanies the report.
\\[2ex]
\textit{Project history} \newline
The work done by Srihari (2000) in implementing learning dependent optical character recognition is an important foundation of this project. The hardware was provided by the Adafruit Industries. Some of the functions in the algorithm associated with handwriting recognition was adapted from Shiffman (2010). The rest of the work documented in this report was my own.
\\[2ex]
\textit{Language editing} \newline
This document has been language edited by a knowledgeable person. By submitting this document in its present form, I declare that this is the written material that I wish to be examined on.

My language editor was \underline{    Mr Bernard Mazimbo    }

% \makebox[3in]{\hrulefill}.

\vspace*{0.5cm}

\begin{tabular}{lp{1cm}ll}
\makebox[3in]{\hrulefill}  &  & \makebox[1.5in]{\hrulefill} \\
\textit{Language editor signature}  &  & \textit{Date}
\end{tabular}

\vspace*{0.5cm}

\textit{Declaration}
\\[2ex]
%I, \makebox[3in]{\hrulefill} understand what 
I, \underline{  Joe Kumbirai Mahlokozela  } understand that
plagiarism is and have carefully
studied the plagiarism policy of the University. I hereby declare that all the
work described in this report is my own, except where explicitly indicated
otherwise. Although I may have discussed the design and investigation with my
study leader, fellow students or consulted various books, articles or the
Internet, the design/investigative work is my own. I have mastered the design
and I have made all the required calculations in my lab book (and/or they are
reflected in this report) to authenticate this. I am not presenting a complete
solution of someone else.

Wherever I have used information from other sources, I have given credit by
proper and complete referencing of the source material so that it can be
clearly discerned what is my own work and what was quoted from other sources.
I acknowledge that failure to comply with the instructions regarding
referencing will be regarded as plagiarism.  If there is any doubt about the
authenticity of my work, I am willing to attend an oral ancillary
examination/evaluation about the work.

I certify that the Project Proposal appearing as the Introduction section of
the report is a verbatim copy of the approved Project Proposal.

\begin{tabular}{lp{1cm}ll}
\makebox[3in]{\hrulefill}  &  & \makebox[1.5in]{\hrulefill} \\
\eprthecandidatename       &  & Date
\end{tabular}

%% End of File.

